Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-17 paper/ijcai16.tex
paper: add section on real attributes.

Substituting the above MILP constraints into the original non-linear
formulation, we obtain the following mixed-integer linear problem:
%
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \nonumber
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M
    \\
        & \;\; \forall \; i \in [k], \forall \; z \in [n] \nonumber
    \\
        & \;\; \qquad p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, w^{i}_z \}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \nonumber
    \\
        & \;\; \qquad p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \nonumber
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \nonumber
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i}_h \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}
}
%
which can be solved by any suitable MILP solver.

@@

\paragraph{Generalization to real variables.}

>>>>

Substituting the above MILP constraints into the original non-linear
formulation, we obtain the following mixed-integer linear problem:
%
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \nonumber
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M
    \\
        & \;\; \forall \; i \in [k], \forall \; z \in [n] \nonumber
    \\
        & \;\; \qquad p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, w^{i}_z \}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \nonumber
    \\
        & \;\; \qquad p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds2}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \nonumber
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i}_h \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}
}
%
which can be solved by any suitable MILP solver.

\paragraph{Linearly dependent real attributes.} In many domains of interest,
items are composed of both Boolean and real-valued attributes, where the latter
depend entirely on the former. For instance, the price, weight and power
consumption of a laptop may be modelled as real-valued attributes, and further
they depend entirely on the choice of components.
%
In this setting, item configurations are composed of two parts: $\vx = (\vx_B;\vx_R)$, where $\vx_B$ is
Boolean and $\vx_R$ is real-valued, and the relation between the two is
entirely described by a non-negative\footnote{Non-negativity is required for
the MILP translation to work.\stefano{better explanation please}} cost matrix
$C\in\bbR^{\text{num costs} \times \text{num bools}}$, such that $\vx_R = C
\vx_B$.  It is straightforward to extend the MILP formulation to this setting,
as follows.

First, we rewrite the weight vector as $\vw = (\vw_B;\vw_R)$. The utility becomes
%
$$ \langle \vw, \vx \rangle = \langle \vw_B, \vx_B \rangle + \langle \vw_R, C \vx_B \rangle = \langle \vw_B + C^\top \vw_B, \vx_B \rangle $$
%
We let $\vv^i := \vw_B^i + C^\top \vv_B^i$, and $q^{ij}_z := (\vw^i_B + C^\top \vw^i_R)_z x^j_z$,
and substitute them in the MILP problem to $\vw$ and $p^{ij}_z$, respectively.
All constraints remain the same, except Eq.~\ref{eq:wbounds2}, which must be
rewritten in terms of $\vv^i$:
%
$$ \forall \; i \in [k] \;.\; (\vw_B^\bot + C^\bot \vw_R) \le \vv^i \le (\vw_B^\top + C^\top \vw_R^\top)$$

\stefano{improve please}

@@
